\documentclass{my_cv}
\usepackage[skins]{tcolorbox}
\usepackage{titlesec}

% \titleformat{\subsection}
%   {\normalfont\large\bfseries}{}{1em}{}
\titlespacing*{\subsection}
  {0pt}{\baselineskip}{0.5\baselineskip}

\begin{document}
\begin{multicols}{2}[
    \titletext{NIU}%
        {Xuezhi}%
        {Student in Mechatronics}%
        {Stockholm, Sweden}%
        {xuezhin@kth.se}%
        {+46 0764334132}%
        {n7729697@gmail.com}%
        {\faGithub \href{https://github.com/n7729697}{n7729697}}%
]
\end{multicols}

\section{\faFileText}{SUMMARY}
Mechatronics grad with extensive experience in complex system design. Skilled in C/C++, Matlab, Python, SolidWorks, AutoCAD, ROS. Fluent in English and Chinese. Passionate about tech innovation.

\begin{multicols}{2}
\section{\faPencil}{EXPERIENCE}

\work{Optimal Gait Control of Soft Quadruped Robot by Model-based Reinforcement Learning / Jan 2023 - Present}%
    {KTH Royal Institute of Technology}%
    {Developed innovative software architecture for a novel soft quadruped robot, optimizing gait patterns through model-based reinforcement learning and collaboration across disciplines.}
\work{Electronically Regulated shut-off Valve for Milking System \href{https://www.kth.se/social/files/63c57e0f3a9f6ce7c9153234/hk22-finalreport-delaval.pdf}{\textit{Report here}}/ Mar 2022 - Jan 2023}%
    {KTH Royal Institute of Technology cooperated with DeLaval Holdings AB}%
    {Led team in designing electronic vacuum control valve, integrating Kalman filter for enhanced reliability and compliance with industry standards.}
\work{Design and Fabrication of MEMS Actuator / Oct 2022 - Jan 2023}%
    {KTH Royal Institute of Technology}%
    {Led team in designing and fabricating optical in-plane switch, employing COMSOL simulations and microfabrication techniques for optimized performance.}%
\work{Monocular Autonomous Drone Systems / Jan 2022 - May 2022}%
    {KTH Royal Institute of Technology}%
    {Led team developing autonomous drone, implementing control algorithms for ROS-based localization, perception, and path planning.}%
% \work{SLAM for Unmanned Vehicle / Jan 2022 - May 2022}%
%     {KTH Royal Institute of Technology}%
%     {Led dynamic team in creating SLAM system for Turtlebot3-based unmanned vehicle, integrating sensor data fusion and designing comprehensive algorithms.}%
\work{Liquid-based Bubble-Driven TENG Generator / Sep 2020 - Jun 2021}%
    {City University of Hong Kong}%
    {Conducted foundational research on liquid-based TENGs, validated and characterized generator's performance, advancing sustainable energy solutions.}%
% \work{Wind turbine blade design and prototyping / Jan 2021 - May 2021}%
%     {City University of Hong Kong}%
%     {Design and manufacture the wind turbine blade for a competition in class and won 2nd place, the prototypes were manufactured based on 3D printing}%
% \work{Automated guided vehicle navigation / Jan 2021 - May 2021}%
    % {City University of Hong Kong}%
    % {Implement the program for a AGV to navigate on the printed desh line, the controller were written by \texttt{C\#} and the embedded microcontroller is LPC1343}%
% \work{Synthesis and Manufacture of Flexible Batteries / Apr 2019 - Jan 2020}%
%     {City University of Hong Kong}%
%     {Developed metal hydroxides for flexible batteries, applied new synthesis method and designed assembly module, collaborated with industry for market implementation.}%
% \work{Utilizing Multiple Sensors to Monitor and Predict Bone Fracture Healing / Sep 2018 - Jan 2019}%
%     {City University of Hong Kong}%
%     {Take in charge of literature review, preparation of prototype, conducting experiments on the prepared prototypes, collect and analyze experiment results etc. Research on multiple sensors cooperation in vivo.}%
% \work{Student Mentor / Sep 2018 - Jun 2019}%
%     {City University of Hong Kong}%
%     {Worked as student mentor for fresh students to guide them adapt to college life, created and delivered instructional materials, coordinated academic counseling workshops, ongoing individual advising services, and customized learning objectives.}%
% \work{Study Tutor / Jan 2018 - May 2018}%
%     {City University of Hong Kong}%
%     {A study tutor on classic physics, took time to understand students’ unique strengths and opportunities, offered feedback using positive reinforcement techniques, taught general test-taking strategies and specific concepts in kinematics, momentum, and energy. Monitored students’ progress throughout academic year.}%
% \work{E-Buddy Project / Sep 2017 - Jun 2018}%
%     {Technology \& Education: Connecting Cultures Hong Kong chapter}%
%     {Brought left-behind children, children with rare diseases, orphans in remote areas knowledge and care by online tutoring and education accompanying. Cumulative duration for 86 hours in 2017-2018, with 10 volunteers and 200 children}%
% \work{Hong Kong Cultural Study Tour / Jan 2018}%
%     {UNLEASHFOUNDATION Limited}%
%     {A study tour for college students from elsewhere to visit and immerse in Hong Kong.}%

\section{\faGraduationCap}{EDUCATION}

\mschool{KTH Royal Institute of Technology - present} %
{Master of Science in Mechatronics Engineering}
\textbf{Master thesis}: Optimal Gait Control of Soft Quadruped Robot by Model-based Reinforcement Learning \\
\textbf{Expected Graduation}: Jan. 2024
    
\school{City University of Hong Kong - 2021} %
{Bachelor of Engineering in Mechanical Engineering} %
{\textit{Control theory, Embedded system, Machine vision, Signal and systems, Thermodynamics, Fluid dynamics, CAD/CAM, MEMS, Manufacturing techniques, Materials, Mechanics etc.}}

\school{National University of Singapore - 2020} %
{Formal exchange} %
{MEMS, Biomaterials, Aerodynamics and Java programming}

% \school{Middlesex University - 2018} %
% {Summer School} %
% {Cultural \& Language Immersion Scheme}

% \section{\faPaintBrush}{OTHER PROJECTS}
% \begin{itemize}[noitemsep]
%     % \item \textbf{Market research} and \textbf{literature review} of trends in digital mental healthcare.
%     \item \textbf{Research} and \textbf{prototyping} in bubble energy liquid-based electricity generator
%     \item \textbf{Synthesis} and \textbf{manufacture} of flexible batteries
%     \item \textbf{Research} in multiple sensors to monitor and predict bone fracture healing
% \end{itemize}

\section{\faList}{SKILLS}
\textbf{Languages:} Native Chinese, fluent English, limited working German, elementary Swedish, C\texttt{++}, Python, C, \textsc{java}, \texttt{C\#}

\noindent\textbf{Tools:} MS Office, Ubuntu, \LaTeX, Adobe Photoshop, Adobe Illustrator, Adobe Premiere Pro, GIMP, SolidWorks, AutoCAD, ROS, MATLAB, Endnote, LS-DYNA, ANSYS, Simplify3D, OriginLab, SPSS, 3D printing, laser cutting, lathe and milling machine, Arduino, STM32 etc.

\section{\faStar}{AWARDS / ACHIEVEMENT}
\begin{itemize}[noitemsep]
    \item CN patent grants (pending), "Novel high-load multi-component metal hydroxide with its synthesis method and application".
    \item CN patent grants (pending), "A flexible battery assembly die and its structural design".
    \item Talent Development Scholarship, Hong Kong SAR Government Scholarship
    \item Second prize in National Finals of the 2019 “Challenge Cup” 
    \item Silver Prize in the National Finals of 2019 “Internet +”
    %\item etc.
\end{itemize}

\section{\faSoccerBallO}{ACTIVITIES / INTERESTS}
Proactive about learning diverse things and happy to discuss those. Curious about how things were featured and how they brought us today. 
\begin{itemize}[noitemsep]
    \item Favorite physical activities would be \textbf{soccer} and \textbf{cycling}. Professor Edmond Ko Cup Soccer 2019 Championship representing Hall 2 of City University of Hong Kong. High school Soccer Match 2016 Championship.
    \item Favorite activities while free would be \textbf{reading} and \textbf{cooking}. Read more than 300 novels of different categories, e.g. science fiction, history, xuanhuan, fantasy etc.
\end{itemize}
% \columnbreak
\end{multicols}

\end{document}
